---
output: github_document
bibliography: bibliography.bib
csl: chicago-author-date.csl
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

# **SaMUraiS**: **S**t**A**tistical **M**odels for the **U**nsupe**R**vised segment**A**t**I**on of time-**S**eries

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/fchamroukhi/SaMUraiS.svg?branch=master)](https://travis-ci.org/fchamroukhi/SaMUraiS)
[![CRAN versions](https://www.r-pkg.org/badges/version/samurais)](https://cran.r-project.org/web/packages/samurais/index.html)
<!-- badges: end -->

samurais is an open source toolbox (available in R and in Matlab) including 
many original and flexible user-friendly statistical latent variable models 
and unsupervised algorithms to segment and represent, time-series data 
(univariate or multivariate), and more generally, longitudinal data which 
include regime changes.

Our samurais use mainly the following efficient "sword" packages to segment 
data: Regression with Hidden Logistic Process (**RHLP**), Hidden Markov Model
Regression (**HMMR**), Piece-Wise regression (**PWR**), Multivariate 'RHLP'
(**MRHLP**), and Multivariate 'HMMR' (**MHMMR**).

The models and algorithms are developed and written in Matlab by Faicel 
Chamroukhi, and translated and designed into R packages by Florian Lecocq, 
Marius Bartcus and Faicel Chamroukhi.

# Installation

You can install the **samurais** package from
[GitHub](https://github.com/fchamroukhi/SaMUraiS) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SaMUraiS")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SaMUraiS", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("samurais")
```

# Usage

```{r, message = FALSE}
library(samurais)
```

<details>
  <summary>RHLP</summary>

```{r, echo = TRUE}
# Application to a toy data set
data("univtoydataset")
x <- univtoydataset$x
y <- univtoydataset$y

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

rhlp <- emRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
               max_iter, threshold, verbose, verbose_IRLS)

rhlp$summary()

rhlp$plot()
```

```{r, echo = TRUE}
# Application to a real data set
data("univrealdataset")
x <- univrealdataset$x
y <- univrealdataset$y2

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

rhlp <- emRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
               max_iter, threshold, verbose, verbose_IRLS)

rhlp$summary()

rhlp$plot()
```
</details>

<details>
  <summary>HMMR</summary>

```{r, echo = TRUE}
# Application to a toy data set
data("univtoydataset")
x <- univtoydataset$x
y <- univtoydataset$y

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

hmmr <- emHMMR(X = x, Y = y, K, p, variance_type, 
               n_tries, max_iter, threshold, verbose)

hmmr$summary()

hmmr$plot(what = c("smoothed", "regressors", "loglikelihood"))
```


```{r, echo = TRUE}
# Application to a real data set
data("univrealdataset")
x <- univrealdataset$x
y <- univrealdataset$y2

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

hmmr <- emHMMR(X = x, Y = y, K, p, variance_type, 
               n_tries, max_iter, threshold, verbose)

hmmr$summary()

hmmr$plot(what = c("smoothed", "regressors", "loglikelihood"))
```

</details>

<details>
  <summary>PWR</summary>

```{r, echo = TRUE}
# Application to a toy data set
data("univtoydataset")
x <- univtoydataset$x
y <- univtoydataset$y

K <- 5 # Number of segments
p <- 3 # Polynomial degree

pwr <- fitPWRFisher(X = x, Y = y, K, p)

pwr$summary()

pwr$plot()
```


```{r, echo = TRUE}
# Application to a real data set
data("univrealdataset")
x <- univrealdataset$x
y <- univrealdataset$y2

K <- 5 # Number of segments
p <- 3 # Polynomial degree

pwr <- fitPWRFisher(X = x, Y = y, K, p)

pwr$summary()

pwr$plot()
```

</details>

<details>
<summary>MRHLP</summary>

```{r, echo = TRUE}
# Application to a toy data set
data("multivtoydataset")
x <- multivtoydataset$x
y <- multivtoydataset[,c("y1", "y2", "y3")]

K <- 5 # Number of regimes (mixture components)
p <- 1 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

mrhlp <- emMRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
                 max_iter, threshold, verbose, verbose_IRLS)

mrhlp$summary()

mrhlp$plot()
```

```{r, echo = TRUE}
# Application to a real data set (human activity recogntion data)
data("multivrealdataset")
x <- multivrealdataset$x
y <- multivrealdataset[,c("y1", "y2", "y3")]

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

mrhlp <- emMRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
                 max_iter, threshold, verbose, verbose_IRLS)

mrhlp$summary()

mrhlp$plot()
```
</details>

<details>
  <summary>MHMMR</summary>

```{r, echo = TRUE}
# Application to a simulated data set
data("multivtoydataset")
x <- multivtoydataset$x
y <- multivtoydataset[,c("y1", "y2", "y3")]

K <- 5 # Number of regimes (states)
p <- 1 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

mhmmr <- emMHMMR(X = x, Y = y, K, p, variance_type, n_tries, 
                 max_iter, threshold, verbose)

mhmmr$summary()

mhmmr$plot(what = c("smoothed", "regressors", "loglikelihood"))
```

```{r, echo = TRUE}
# Application to a real data set (human activity recognition data)
data("multivrealdataset")
x <- multivrealdataset$x
y <- multivrealdataset[,c("y1", "y2", "y3")]

K <- 5 # Number of regimes (states)
p <- 3 # Dimension of beta (order of the polynomial regressors)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter <- 1500
threshold <- 1e-6
verbose <- TRUE

mhmmr <- emMHMMR(X = x, Y = y, K, p, variance_type, n_tries, 
                 max_iter, threshold, verbose)

mhmmr$summary()

mhmmr$plot(what = c("smoothed", "regressors", "loglikelihood"))
```

</details>

# Model selection

samurais also implements model selection procedures to select an optimal model 
based on information criteria including **BIC**, **AIC** and **ICL**.

The selection can be done for the two following parameters:

 * **K**: The number of regimes (segments);
 * **p**: The order of the polynomial regression.

Instructions below can be used to illustrate the model on provided simulated 
and real data sets.

<details>
  <summary>RHLP</summary>

Let's select a RHLP model for the following time series:

```{r, message = FALSE}
data("univtoydataset")
x = univtoydataset$x
y = univtoydataset$y

plot(x, y, type = "l", xlab = "x", ylab = "Y")
```

```{r, message = FALSE}
selectedrhlp <- selectRHLP(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedrhlp$plot(what = "estimatedsignal")
```

</details>

<details>
  <summary>HMMR</summary>

Let's select a HMMR model for the following time series:

```{r, message = FALSE}
data("univtoydataset")
x = univtoydataset$x
y = univtoydataset$y

plot(x, y, type = "l", xlab = "x", ylab = "Y")
```

```{r, message = FALSE}
selectedhmmr <- selectHMMR(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedhmmr$plot(what = "smoothed")
```

</details>

<details>
<summary>MRHLP</summary>

Let's select a MRHLP model for the following multivariate time series:

<br />

```{r}
data("multivtoydataset")
x <- multivtoydataset$x
y <- multivtoydataset[, c("y1", "y2", "y3")]
matplot(x, y, type = "l", xlab = "x", ylab = "Y", lty = 1)
```

```{r, message = FALSE}
selectedmrhlp <- selectMRHLP(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedmrhlp$plot(what = "estimatedsignal")
```

</details>

<details>
  <summary>MHMMR</summary>

Let's select a MHMMR model for the following multivariate time series:

```{r}
data("multivtoydataset")
x <- multivtoydataset$x
y <- multivtoydataset[, c("y1", "y2", "y3")]
matplot(x, y, type = "l", xlab = "x", ylab = "Y", lty = 1)
```

```{r, message = FALSE}
selectedmhmmr <- selectMHMMR(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedmhmmr$plot(what = "smoothed")
```

</details>

# References
