---
output: github_document
bibliography: bibliography.bib
nocite: '@*'
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

# **SaMUraiS**: **S**t**A**tistical **M**odels for the **U**nsupe**R**vised segment**A**tion of t**I**me **S**eries

SaMUraiS is a toolbox including many flexible user-friendly and original 
statistical latent variable models and unsupervised algorithms to segment and 
represent, time-series data (univariate or multivariate), and more generally, 
longitudinal data which include regime changes.

Our SaMUraiS use mainly the following efficient "sword" packages to segment 
data:

* RHLP;
* MRHLP;
* HMM/HMMR;
* MHMMR;
* PWR.

The models and algorithms are developed and written in Matlab by Faicel 
Chamroukhi, and translated and designed into R packages by Florian Lecocq, 
Marius Bartcus and Faicel Chamroukhi.

<!-- badges: start -->
<!-- badges: end -->

# Installation

You can install the **samurais** package from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SaMUraiS")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/SaMUraiS", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("samurais")
```

# Usage

# References
